Calculating Entropies With Nested Sampling

### 2017-01-19 paper/ms.tex
Paragraph about volume of an n-ball

>>>>

If the distance function $d(\x', \x)$ is chosen to be Cartesian,
the constraint $d(\x', \x) < \epsilon$ corresponds to a ball in the space
of possible $\x'$ values.
The log-volume of a ball of radius $\epsilon$ in $n$ dimensions is
\begin{align}
\log V(\epsilon; n) &= \frac{n}{2}\log \pi
                        - \log \Gamma\left(\frac{n}{2} + 1\right)
                        + n \log \epsilon,
\end{align}
and provides the conversion factor between the differential entropy and
the entropy actually computed from the algorithm.
